---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
pkgload::load_all()
```

# wrswoR.benchmark

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![R build status](https://github.com/krlmlr/wrswoR.benchmark/workflows/rcc/badge.svg)](https://github.com/krlmlr/wrswoR.benchmark/actions)
[![CRAN status](https://www.r-pkg.org/badges/version/wrswoR.benchmark)](https://CRAN.R-project.org/package=wrswoR.benchmark)
<!-- badges: end -->

The goal of wrswoR.benchmark is to provide benchmark data for [{wrswoR}](https://github.com/krlmlr/wrswoR), a package with different implementations of weighted random sampling without replacement.

## Installation

You can install the released version of wrswoR.benchmark from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("wrswoR.benchmark")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("krlmlr/wrswoR.benchmark")
```
## Example

The package contains several datasets, this is one of them:

```{r example}
library(wrswoR.benchmark)
timings
```
